Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-17 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
Notice that the set of 1-dimensional projectors mapping to impossible,
$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\phi}\in\mathbb{C}^{3}\middle|\bar{\mu}(\proj{\phi})=\imposs\right\} $
provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
Since for any two states~$\ket{\phi_{0}},\ket{\phi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
we have $\bar{\mu}(\proj{\phi_{0}})=\bar{\mu}(\proj{\phi_{1}})=\imposs$
so that $\bar{\mu}$ might be induced by the state $\ket{\phi_{0}}\times\ket{\phi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}.

>>>>

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
Notice that the set of 1-dimensional projectors mapping to impossible,
$\bar{\mu}^{-1}\left(\imposs\right)=\left\{ \ket{\psi}\in\mathbb{C}^{3}~\middle|~\bar{\mu}(\proj{\psi})=\imposs\right\} $
provides a appealing way to suggest a possible state inducing $\bar{\mu}$.
Since for any two states~$\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\bar{\mu}^{-1}\left(\imposs\right)$,
we have $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$
so that $\bar{\mu}$ might be induced by the state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}. Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are
normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
when there is no confusion. There are 4 different cases.
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$. Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states which are in core.

As we did in Fig.~\ref{fig:three-dimensional-4-value},
